---
output: pdf_document

---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```



# FE590.  Assignment #1.


## `r format(Sys.time(), "%Y-%m-%d")`

I pledge on my honor that I have not given or received any unauthorized assistance on this assignment/examination. I further pledge that I have not copied any material from a book, article, the Internet or any other source except where I have expressly cited the source.

By filling out the following fields, you are signing this pledge.  No assignment will get credit without being pledged.

Name:Zongqishen

CWID:10479206

Date:02/05/2022

# Question 1

## Question 1.1
```{r}
CWID = 10479206 #Place here your Campus wide ID number, this will personalize
#your results, but still maintain the reproduceable nature of using seeds.
#If you ever need to reset the seed in this assignment, use this as your seed
#Papers that use -1 as this CWID variable will earn 0's so make sure you change
#this value before you submit your work.
personal = CWID %% 10000
set.seed(personal)
```
Generate a vector `x` containing 10,000 realizations of a random normal variable with mean 1.0 and standard deviation 3.0, and plot a histogram of `x` using 100 bins.

(Note that the following two fields can be added wherever you desire to show a solution.  You can use the first for a written response, and the second for showing R code and its output.  Some questions will require just one, and some both.  I will not always provide you with these, but you can add them at your discretion whereven necessary.  If it makes sense to do the R code first then thats fine.  If you want to include multiple of each, thats ok too.  Do what you feel is necessary to answer the question fully.)

## \textcolor{red}{Solution:} 

```{r}
#response
x <- rnorm(10000,mean = 1, sd = 3)
hist(x,breaks = 100)
#or
#x <- data.frame(x)
#ggplot(x, aes(x)) +            # ggplot2 histogram with manual bins
 # geom_histogram(bins = 100)
```


## Question 1.2
Calculate the mean and standard deviation of these 10000 values.  Do your answers make sense?

## \textcolor{red}{Solution:}

```{r}
# my response
# Yes it does make sense 
mean(x)
sd(x)
```





## Question 1.3
Using the `sample` function, take out 10 random samples of 500 observations each (with replacement).  Create a vector of the means of each sample.  Calculate the mean of the sample means and the standard deviation of the sample means.  What do you observe about these results?

## \textcolor{red}{Solution:}

```{r}
# Enter your R code here!
m <- rep(0, 10)
for (i in 1:10) {
m[i] <- mean(sample(x, 500))
}
Mean <- mean(m)
print(Mean)

Sd <- sd(m)
print(Sd)
#the mean is always around 1
#the sd is always around 0.1
```




#Question 2

##Question 2.1

Create a script that creates a vector of the values from 1 to 100 using a for loop.

## \textcolor{red}{Solution:}

```{r}
# Enter your R code here!
v = NULL
for (num in 1:100){
  v = cbind(v,num)
}
v 
#for your convenient i change the type of output as array

```

##Question 2.2

Create a script that creates a vector of the first 20 Fibbonaci numbers.

## \textcolor{red}{Solution:}

```{r}
Fibonacci <- numeric(20)
Fibonacci[1] <- Fibonacci[2] <- 1
for (i in 3:20) Fibonacci[i] <- Fibonacci[i - 2] + Fibonacci[i - 1]
print("First 20 Fibonacci numbers:")
print(Fibonacci)

```






# Question 3
Download the FinDataAdjCl.csv data set from the Canvas shell, as you'll need it for this assignment

## Question 3.1

Load the csv file and use the summary command to analyze three stocks from this data set (your choice which 3)



```{r message=FALSE}
# Enter your R code here!
library(gdata)
FinDataAdjCl <- read.csv("FinDataAdjCl.csv", stringsAsFactors = FALSE)
typeof(FinDataAdjCl$Date)
summary(FinDataAdjCl[,c(4,5,6)])
```



## Question 3.2

Split the data into two pieces, one for the dates from 2015 and earlier and the other for the dates after 2015.  Use these subsets to rerun your summary command for each group for the same stocks you used in 3.1

## \textcolor{red}{Solution:}

```{r}
# Enter your R code here!
Finsubup <- FinDataAdjCl[1:which(FinDataAdjCl$Date == "1/2/2015"),c(4,5,6)]
Finsubdown <- FinDataAdjCl[(which(FinDataAdjCl$Date == "1/2/2015")+1):nrow(FinDataAdjCl),c(4,5,6)]
summary(Finsubup)
summary(Finsubdown)
```

## Question 3.3

What do you see in these results? Are the company's prices changing?  Do you think this is just inflation or is it more noticable in one or the other?

## \textcolor{red}{Solution:}

```{r}
# Enter your R code here!
#stock GOOG are highly changed. Even GOOG min stock price is 492 which is almost same with 
#the price after 2015, but median price and MAX price before 2015 is much lower than price after 2015

```



#Question 4

##Question 4.1

Download and use the "fakedataeasy.csv" file found under Modules section of Canvas.  Using this data set, find the mean and standard deviation of each of the variables in this data set.  

## \textcolor{red}{Solution:}

```{r}
# Enter your R code here!
library(gdata)
fakedataeasy <- read.csv("fakedataeasy.csv")
fakedataeasy <- as.data.frame(fakedataeasy)

means <- NULL
sds <- NULL
for (i in 1:length(fakedataeasy)) {
    means <-cbind(means,mean(fakedataeasy[,i]))
    sds <- cbind(sds,sd(fakedataeasy[,i]))
}

mat <- as.data.frame(matrix(0,2,5))
row.names(mat) <-c("mean", "sd")
names(mat) <- names(fakedataeasy)

mat[1,] <- means
mat[2,] <- sds
print(mat)
```

